\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

\hinttext{While not required, it is a good idea to write a couple of paragraphs to thank the people that helped you. Try to stay within the margins of this page. There is no need to write a novel. You can structure this any way you like. The text below should be considered as an example to give you an approximate idea what this section may look like. Please do not simply copy. Write your own acknowledgments! This can be very personal!}

This work would not have been possible without all the help and support provided by others. During my time here in Australia and in particular at {\myUni}, I had the honor of meeting a lot of interesting people, many of whom became friends. To all of you, I hereby say: \emph{Thank You for everything! This would not have been possible without you!} However, there are a couple of individuals who deserve special mention.

Firstly, I would like to thank my supervisor \textbf{\myProfTitle} \textbf{\myProfFirstName} \textbf{\myProfLastName} for ... \hinttext{well, you should know why. You supervisors are definitely going to read this. What exceptional traits of them helped you to further your research or were there memorable moments during your candidature that you would like them to recall?}

I also want to thank my co-supervisor \textbf{\myOtherProfTitle} \textbf{\myOtherProfFirstName} \textbf{\myOtherProfLastName} for ... \hinttext{well, you should know why. You supervisors are definitely going to read this. What exceptional traits of them helped you to further your research or were there memorable moments during your candidature that you would like them to recall?}

Furthermore, I also want to thank all the members of the \emph{La Trobe student society / club / research group} \hinttext{(whichever applies)} for the many discussions and valuable inputs along the way. A special thanks goes to \textbf{Proofreader's name} for helping me improve my English grammar \hinttext{(if English is not your mother tongue you should get your thesis checked!)}; \textbf{Name of individual or organization that supported you} for ... \hinttext{(try to sum up in one sentence what they did to aid your research, personal development, etc.)}; and \textbf{Author who wrote letter of support no.~1}, \textbf{Author who wrote letter of support no.~2} and \textbf{Name of the research coordinator at the time} for their support of my scholarship application, without which my candidature would not have been possible.

I also want to thank my wife/husband/partner \textbf{Spouse's name}, who took care of our son/daughter/kids during the many days and nights that I spent at the university and made sure that I had a comfy home to go back to every day. And of course\textemdash{}last but not least\textemdash{}I want to thank my son/daughter/kids \textbf{Child Name 1}, \textbf{Child name 2} and \textbf{Child name 3} for \hinttext{... well, you should know why!}

\hinttext{Hence, generally speaking, I would start with a blanket statement in the first paragraph. This way, you have covered all entities that are not explicitly named thereafter. Then, you should address all people that provided academic support (supervisor, co-supervisor, the research group, individuals that helped you). Then, give credit to the people that believed that you and supported your candidature before you actually started your research. In particular, I would suggest mentioning the 2-3 people that provided letters of support and the responsible research coordinator. Finally, add one paragraph for individuals that provided significant support that is not directly associated with your research (\eg you spouse/sweetheart).}