\chapter*{Publications}
\addcontentsline{toc}{chapter}{Publications}

\hinttext{This page is mandatory. The content and structure must comply with the regulations of your school or department. Rules and regulations may change during your candidature. Please consult the \emph{guidelines for preparing a thesis}\footnote{\url{https://www.latrobe.edu.au/researchers/grs/hdr/candidature/forms-and-resources}} to make sure you got things right. Talk with your supervisor or research coordinator if you intend to deviate from the standard.}

This thesis includes work by the author that has been published or accepted for publication. These publications are the own work of the author of this thesis, and the author has the permission of the publishers to reproduce the contents of these publications for academic purposes.

In particular, some data, ideas, opinions and figures presented in this thesis have previously appeared or may appear shortly after the submission of this thesis as follows:
\begin{itemize}

  \item \hinttext{You MUST list all you publications that are quoted verbatim throughout your thesis here! Make sure this is complete to protect yourself from the accusation of academic misconduct. Self-plagiarism is also plagiarism! Make sure that you have the permission of the respective journals and your co-authors if you intend to quote passages from papers verbatim.}
  
  \item Feyd-Rautha Harkonnen, Glossu Rabban ``\textbf{How to use Ixian Probes to Extract Memories from Tleilaxu Masters}'' accepted for publication in \emph{Technological and Scientific Journal of the Spacing Guild}, ISSN: 1234-5678, DOI: \href{https://en.wikipedia.org/wiki/Spacing_Guild}{99.8765/SPACE.2018.312134}
  
  \item Feyd-Rautha Harkonnen, Shaddam Corrino, Piter De Vries ``\textbf{A novel approach to use the Holtzmann Effect to break through shield walls}'' published in \emph{League Worlds Joint Engineering Society Journal}, ISSN: 9122-9122, DOI: \href{https://en.wikipedia.org/wiki/Organizations_of_the_Dune_universe#Landsraad}{00.1234/LRAAD.2018.123344}
  
  \item Piter De Vries, Feyd-Rautha Harkonnen ``\textbf{Why the Spice must flow?}'' \textendash{} Working draft currently under preparation for submission. \hinttext{This is not required, but it may be useful in case your thesis is accepted earlier than your paper.}
  
\end{itemize}
Except where reference is made in the text of the thesis, this thesis contains no other material published elsewhere or extracted in whole or in part from a thesis accepted for the award of any other degree or diploma. No other person's work has been used without due acknowledgment in the main text of the thesis. This thesis has not been submitted for the award of any degree or diploma in any other tertiary institution.

